\documentclass[sigplan,nonacm]{acmart}
\settopmatter{printfolios=true}
\usepackage{graphicx} % Required for inserting images
\usepackage[normalem]{ulem}

\title{Related Works}
\author{Mark Madler}
\begin{document}
\maketitle
%All are related to some degree -- so they are organized as follows:

%                       REPLICATED KVS
%------------------------------------------------------------------------------------

\section{Replicated Data Stores over RDMA}

    \subsection{Kite: efficient and available release consistency for the datacenter}
    This is the real entry paper. This is a replicated KVS over RDMA.\cite{Gavrielatos-PPoPP-2020}

    \subsection {Hermes: A Fast, Fault-Tolerant and Linearizable Replication Protocol}
    Fault tolerant protocol for replication of datastore. Linearizable. \cite{Katsarakis-ASPLOS-2020}

    \subsection {Hamband: RDMA Replicated Data Types}
    This is obviously a replicated system.\cite{Houshmand-PLDI-2022}

    \subsection{FaRM: Fast Remote Memory}
    Super similar to the entry paper. A lot of other papers call it DSM so 
    I am not totally sure about this. I think this still caches data at the page level.\cite{Dragojevic-NSDI-2014}

    \subsection{FaRMv2: Fast General Distributed Transactions with Opacity}
    Just like FaRM but with opacity. Also providing strict serializability.\cite{Shamis-SIGMOD-2019}

%                       DSM OVER RDMA
%-----------------------------------------------------------------------------------

\section {DSM systems}

    \subsection{Scaling out NUMA-Aware Applications with RDMA-Based Distributed Shared Memory: MAGI}
    Page-based DSM again. \cite{Hong-JCST-2019}

    \subsection{Gengar: An RDMA-based Distributed Hybrid Memory Pool}
    This is object based dsm over rdma but with non-volatile memory as well using Intel Optane. Seems to 
    also use this lease assignment idea like in \cite{Endo-IPDRM-2020} but is not page based.\cite{Duan-ICDCS-2021}

    \subsection{MENPS: A Decentralized Distributed Shared Memory Exploiting RDMA}
    \begin{itemize}
        \item Page based DSM
        \item Special Diff merging and page sharing
        \item Combine write notices and logical leases (what is that?)\cite{Endo-IPDRM-2020}
    \end{itemize}

    \subsection{Argo DSM (Turning Centralized Coherence and Distributed Critical-Section Execution on their Head: A New Approach for Scalable Distributed Shared Memory)}
    Page-based DSM again but directory coherence. This was maybe the first RDMA-based DSM paper, 
    at least thats what the authors allude to.\cite{Kaxiras-HPDC-2015}

    \subsection{Evaluation of RDMA opportunities in an Object-Oriented DSM}
    entry paper? Interesting result is that it proves that invalidation protocols are better suited 
    for distributed systems. \cite{Veldema-LCPC-2007}

%                       OTHER STUFF
%-----------------------------------------------------------------------------------

\section{Closely Related Works object based / not page-level granularity}

    \subsection {Odyssey: The Impact of Modern Hardware on Strongly-Consistent Replication Protocols} %where to put this
    This is the larger project that Kite is a part of. Not really an implemented work itself but it is sort of 
    a survey of protocols used.\cite{Gavrielatos-EuroSys-2021}

    \subsection{Efficient Distributed Memory Management with RDMA and Caching } %where to put this
    cache-line granularity.\cite{Cai-VLDB-2018} 

    \subsection{Distributed Shared Object Memory}%where to put this
    object based granularity, release consistency... too old for RDMA\cite{Guedes-WWOSIII-1993}

    \subsection{Scalable RDMA performance in PGAS languages}
    This paper is for PGAS languages. Has an address hash table similar to LOCO for remote lookups.\cite{Farreras-IPDPS-2009}
%-----------------------------------------------------------------------------------

%Loosely Related / Line of Work 
\section{Loosely Related but Evaluated}
\subsection{TreadMarks: shared memory computing on networks of workstations}
Was implemented over IP, lazy release consistency I think. Not sure of granularity yet.\cite{Amza-Usenix-1994}

\subsection{CoRM: Compactable Remote Memory over RDMA}
page based I think (re-read this)\cite{Taranov-ICMD-2021}

\subsection{LITE Kernel RDMA Support for Datacenter Applications}
This is page based DSM using the kernel. \cite{Tsai-SOSP-2017}


\subsection {GiantVM: A Novel Distributed Hypervisor for Resource Aggregation with DSM-aware Optimizations}
Page-based DSM again but also works over TCP and RDMA\cite{Jia-ACO-2022}



%------------------------------

%I looked these up but they were too far off to compare at all
\section{Evaluated but not Related}
\subsection{Rcmp: Reconstructing RDMA-Based Memory Disaggregation via CXL}
page based and uses CXL, not comparable\cite{Wang-ACO-2024}

%--------------------------------------------------------------

\bibliographystyle{acm}
\bibliography{relworks}
\end{document}